# Logistic Regression Classification


### Importing the dataset
```{r}
dataset = read.csv('Social_Network_Ads.csv')
dataset = dataset[3:5]
```


### Splitting the dataset into the Training Set and Test Set
```{r}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 3/4)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```


### Feature Scaling
```{r}
training_set[, 1:2] = scale(training_set[, 1:2])
test_set[, 1:2] = scale(test_set[, 1:2])
```


### Fitting Logistic Regression (Classification) Model into the Training Set
```{r}
classifier = glm(formula = Purchased ~ .,
                 family = binomial,   # Very important 
                 data = training_set)
```


### Predicting the results
```{r}
prob_pred = predict(classifier,
                    type = 'response',   # Very important
                    newdata = test_set[-3])
y_pred = ifelse(prob_pred > 0.5,   # the condition
                1,   # result if the condition is true
                0)   # result if the condition is false 
```
 

### Fetching the observations from Test Set
```{r}
y_test = test_set$Purchased
```


### Creating the Confusion Matrix 
```{r}
cm = table(y_test, y_pred)
print("The confusion matrix is: ")
print(cm)
```


### Calculating the accuracy of the model
```{r}
accuracy_vector = ifelse(y_test == y_pred,
                         1,
                         0)
accuracy_score = sum(accuracy_vector) / length(accuracy_vector)
accuracy_score_percent = 100.00 * accuracy_score
sprintf("The accuracy score is %.2f%%", accuracy_score_percent)
```


### Visualizing Training Set Results
```{r}
# install.library('Rfast')
library(Rfast)
set = training_set
X1 = seq(min(set[,1]) - 1,
         max(set[,1]) + 1,
         by = 0.01)
X2 = seq(min(set[,2]) - 1,
         max(set[,2]) + 1,
         by = 0.01)
grid_set = expand.grid(X1,X2)
colnames(grid_set) = c('Age',
                       'EstimatedSalary')
prob_set = predict(classifier,
                   type = 'response',
                   newdata = grid_set)
y_grid = ifelse(prob_set > 0.5,
                1,
                0)
plot(set[, -3],
     main = 'Logistic Regression (Training Set)',
     xlab = 'Age (Scaled)', ylab = 'Estimated Salary (Scaled)',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, 
        matrix(as.numeric(y_grid), length(X1), length(X2)),
        add = TRUE)
points(grid_set, 
       pch = '.',
       col = ifelse(y_grid == 1,
                    'springgreen3',
                    'tomato'))
points(set,
       pch = 21,
       bg = ifelse(set[,3] == 1,
                   'green4',
                   'red3'))
```


### Visualizing Test Set Results
```{r}
library(Rfast)
set = test_set
X1 = seq(min(set[,1]) - 1,
         max(set[,1]) + 1,
         by = 0.01)
X2 = seq(min(set[,2]) - 1,
         max(set[,2]) + 1,
         by = 0.01)
grid_set = expand.grid(X1,X2)
colnames(grid_set) = c('Age',
                       'EstimatedSalary')
prob_set = predict(classifier,
                   type = 'response',
                   newdata = grid_set)
y_grid = ifelse(prob_set > 0.5,
                1,
                0)
plot(set[, -3],
     main = 'Logistic Regression (Test Set)',
     xlab = 'Age (Scaled)', ylab = 'Estimated Salary (Scaled)',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, 
        matrix(as.numeric(y_grid), length(X1), length(X2)),
        add = TRUE)
points(grid_set, 
       pch = '.',
       col = ifelse(y_grid == 1,
                    'springgreen3',
                    'tomato'))
points(set,
       pch = 21,
       bg = ifelse(set[,3] == 1,
                   'green4',
                   'red3'))
```
